% Jake-styled resume (header slimmed; body intact)
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}\fancyhf{}\renewcommand{\headrulewidth}{0pt}\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}\addtolength{\topmargin}{-.5in}\addtolength{\textheight}{1.0in}

\urlstyle{same}\raggedbottom\raggedright\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Matthew Fehr} \\ \vspace{1pt}
    \small 310-467-8139 | matthewfehr2004@gmail.com
\end{center}

\section{Education}
California State University, Long Beach
BS Computer Science (AI/ML Track) - 4.0 GPA
August 2022-May 2026
\resumeItemListStart
    \resumeItem{Member of the ICPC Competitive Programming Team, applying knowledge of advanced data structures and algorithms to solve complex challenges.}
\resumeItemListEnd

\section{Experience}
\textbf{Team Lead / Project Manager} | BRDG Innovation Challenge
\hfill May 2025-August 2025
\resumeItemListStart
    \resumeItem{Led a multidisciplinary team of 7 in an innovative sustainability challenge, securing 2nd place statewide by designing a modular aeroponic tower system that reduced agricultural water use by up to 99\%.}
    \resumeItem{Effectively managed the project lifecycle, including a \$2500 budget and technical requirements, to deliver a comprehensive business and software solution.}
    \resumeItem{Engineered a full-stack marketplace platform, enabling a community-driven ecosystem for designing and sharing modular components; features included user authentication, reviews, and persistent data storage.}
\resumeItemListEnd

\section{Projects}
\textbf{Volleyball Rotation Tool} | (TypeScript, React, Tailwind, Firebase)
\resumeItemListStart
    \resumeItem{Developed an interactive web application for volleyball coaches and teams to manage complex rotations, supporting workflows for over 5 teams.}
    \resumeItem{Implemented a dynamic, PDF-exportable canvas overlay system with annotation capabilities.}
    \resumeItem{Leveraged cloud-based Firebase services (Auth and Firestore) for user account management and persistent data storage, ensuring data integrity and accessibility.}
\resumeItemListEnd

\textbf{Peer-to-Peer Network} | (Python, Docker, Flask, REST API)
\resumeItemListStart
    \resumeItem{Architected and built a scalable, distributed peer-to-peer messaging system in Python, deploying 24 containerized nodes with Docker for demonstrating system resilience and scale.}
    \resumeItem{Implemented fault-tolerant peer discovery and data synchronization using RESTful APIs and multi-threading, addressing key challenges in building decentralized systems.}
\resumeItemListEnd

\textbf{Anime Recommender} | (Python, FastAPI, React, Scikit-Learn, Selenium, Render, Vercel)
\resumeItemListStart
    \resumeItem{Engineered and deployed a hybrid recommendation system using collaborative (SVD) and content-based (TF-IDF) filtering algorithms, achieving a low RMSE of 0.85.}
    \resumeItem{Built a Python-based web scraper to collect large user-rating datasets from MyAnimeList, enriching the data via the Jikan API for improved recommendation accuracy.}
\resumeItemListEnd

\textbf{GitHub Agent} | (DAIN AI, GitHub, Typescript)
\resumeItemListStart
    \resumeItem{Developed a software agent for a hackathon challenge that automated GitHub workflows, including merging pull requests and managing repository structures, by leveraging the GitHub REST API.}
\resumeItemListEnd

\textbf{Sport Classifier} | (Colab, Python, Tensorflow, Scikit-learn)
\resumeItemListStart
    \resumeItem{Achieved 99\% classification accuracy on a large dataset (>1000 images) by training a CNN model with TensorFlow; enhanced performance through transfer learning and data augmentation.}
\resumeItemListEnd

\section{Technical Skills}
\resumeItemListStart
    \resumeItem{\textbf{Languages:} C++, Python, SQL, JavaScript, HTML/CSS}
    \resumeItem{\textbf{Frameworks/Libraries:} Scikit-learn, Pandas, TensorFlow, NumPy, React, Flask, Matplotlib}
    \resumeItem{\textbf{Tools \& Technologies:} Git, Docker, Firebase, REST APIs, Ubuntu, Vercel, Render}
\resumeItemListEnd

\end{document}
